---
title: "Example SpatialFeatureExperiment datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example SpatialFeatureExperiment datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SFEData)
```

Example spatial transcriptomics datasets with [Simple Features](https://r-spatial.github.io/sf/) annotations as `SpatialFeatureExperiment` objects. In the first version, the only full dataset is a mouse skeletal muscle Visium dataset 2 days after notexin injury from [Large-scale integration of single-cell transcriptomic data captures transitional progenitor states in mouse skeletal muscle regeneration](https://doi.org/10.1038/s42003-021-02810-x). Two small subsets of the full dataset are also included for quick demos. More datasets will be added in later versions.

This package is used extensively in examples and vignettes of the `SpatialFeatureExperiment` and `Voyager` packages. For now, the basic usage:

```{r}
sfe <- McKellarMuscleData(dataset = "small")
```

```{r}
sessionInfo()
```
