---
title: "Example SpatialFeatureExperiment datasets"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Example SpatialFeatureExperiment datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Installation

This package can be installed from Bioconductor with the following command:
```{r, eval=FALSE}
if (!requireNamespace(BiocManager, quietly = TRUE)) install.packages("BiocManager")
BiocManager::install("SFEData")
```

# Usage

```{r setup}
library(SFEData)
```

Example spatial transcriptomics datasets with [Simple Features](https://r-spatial.github.io/sf/) annotations as `SpatialFeatureExperiment` objects. These are the datasets available from this package and functions to download the datasets:

Visium:

* Full Visium dataset of the first time point, including spots outside tissue (`McKellarMuscleData()`)
* Small subset of the full Visium dataset for function examples. (`McKellarMuscleData()`)
* A second small subset of the full Visium dataset with a different `sample_id` used for function examples involving multiple samples (`McKellarMuscleData()`)

Slide-seq2:

* Slide-seq2 human melanoma brain metastasis dataset (`BiermannMelaMetasData()`)
* Slide-seq2 human melanoma extracranial metastasis dataset (`BiermannMelaMetasData()`)

Xenium:

* 10X Xenium formalin fixed paraffin embedded (FFPE) Xenium dataset for human
breast cancer (2 biological replica, `JanesickBreastData()`)

CosMX:

* Nanostring CosMX FFPE human non small cell lung cancer data (`HeNSCLCData()`)

MERFISH:

* Vizgen MERFISH mouse liver data (`VizgenLiverData`)

This package is used extensively in examples and vignettes of the `SpatialFeatureExperiment` and `Voyager` packages. The same function is used for different samples from the same study, and the `dataset` argument determines which sample is downloaded:
```{r}
sfe <- McKellarMuscleData(dataset = "small")
```

```{r}
sessionInfo()
```
